---
output: 
  md_document:
    variant: markdown_github
---

# Overview

It's fall, so let's get festive AND creative at this meeting.  Let's take a
lighthearted look at some data about peoples' favorite Halloween candies.  We 
would like you to train a model that can predict which candies people will 
prefer.  This repository contains training data as well as predictor variables 
for a test dataset.  The repository does not contain the answers. The best
predictions (as measured by MSE) will receive simple prizes.  The best 
visualizations of the training data will also receive simple prizes.

We have also provided some sample R scripts you can use to get started.
- ```load_data.R``` will load data
- ```visualizations.R``` shows some interesting visualizatons you can think 
  about, to get started.
- ```sample predictions.R``` shows an example of how we would like you to build
 predictions.
 
Good luck and have fun!!


# The data

## train.csv

Use this data to train a model to predict ```winpercent```.  Alternatively, 
try to come up with the most interesting or informative visualization of this 
data.

```{r}
head(read.csv('train.csv'))
```

## test.csv

This data contains the predictor variables for a few candies, for which we 
would like you to use the model you built to predict the missing variable,
```winpercent```.  We will check your answers and award prizes to the model 
that has the best predictions.

```{r}
head(read.csv('test.csv'))
```
